---
title: "Project_2_part1"
author: "yaru peng"
date: "4/25/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(stringr)
library(dplyr)
library(ggplot2)

url1 <- "http://www.ndbc.noaa.gov/view_text_file.php?filename=mlrf1h"
url2 <- ".txt.gz&dir=data/historical/stdmet/"
years <- c(1987:2017)
urls <- str_c(url1, years, url2, sep = "")
filenames <- str_c("mr", years, sep = "")
N <- length(urls)

for (i in 1:N){
  suppressMessages(
    assign(filenames[i], read_table(urls[i], col_names = TRUE))
  )
  file <- get(filenames[i])
  colnames(file)[1] <-"YYYY"
  if(!is.numeric(file[1,1])){
    file <- file[2:nrow(file),]
    file$YYYY <- as.numeric(file$YYYY)
  }
  file$YYYY <- ifelse(as.numeric(file$YYYY%/%100)<1, file$YYYY+1900, file$YYYY)
  file <- file %>% filter(hh==12)
    

   
  if(i == 1){
    MR <- file %>% select(YYYY, MM, DD, hh, ATMP, WTMP)
  }
  else{
    MR <- rbind.data.frame(MR, file %>% select(YYYY, MM, DD, hh, ATMP, WTMP))
    }
}

MR$MM <- as.numeric(MR$MM)
MR$DD <- as.numeric(MR$DD)
MR$hh <- as.numeric(MR$hh)
MR$ATMP <- as.numeric(MR$ATMP)
MR$WTMP <- as.numeric(MR$WTMP)
MR <- MR %>% 
  filter(ATMP<99) %>% 
  filter(WTMP<99)

raw.data <- MR %>% 
  select(YYYY,ATMP, WTMP,  MM, DD) %>% 
  mutate(date=as.Date(paste(as.character(MM), "/", as.character(DD), "/", as.character(YYYY), sep=""), format = "%m/%d/%Y")) %>% 
  select(date, ATMP, WTMP) 
  
tidy.data <- raw.data %>% 
  gather(key = "Temp", value = "Celsius", -date)

```

## Introduction

- Find the webside for NOAA Weather Station buoy 46035 at 57.026 N 177.738 W
- Read, Clean, and organize the data to produce a time series
- Visualize and explore the data


## Temperature change of sea and air over time 

```{r}
ggplot(data = tidy.data, aes(x=date, y=Celsius, color = Temp))+geom_line()+
  xlab("Year") +
  ylab("Temperature") +
  ggtitle("Temperature over time")
```


## Air temperature Trend

```{r}

ggplot(data = raw.data, aes(x = date, y=ATMP))+
  geom_line()+
  stat_smooth(method = lm)+
  xlab("Year")+
  ylab("Temperature(Celcius)")+
  ggtitle("air")
```

## Air trend statistics test

```{r}
stat.air <- lm(ATMP~date, data = raw.data)
summary(stat.air)
```


## Sea Temperature Trend

```{r}
ggplot(data = raw.data, aes(x = date, y=WTMP))+
  geom_line()+
  stat_smooth(method = lm)+
  xlab("Year")+
  ylab("Temperature(Celcius)")+
  ggtitle("sea")

```

## Sea trend statistics test
```{r}
stat.sea <- lm(WTMP~date, data = raw.data)
summary(stat.sea)

```

## Conclusion

From the statistics test and graph, we can observe that sea temperature trend has a P-value less .05 thus we can conclude that sea temperature has increased over time. However on other hand, air temperature's p-value is greater than .05 thus we cannot say that mean has significantly increased over time.

